Ellicular galaxies and their (non over-massive) black holes

### 2015-09-21 papers/ellicular/ellicular.tex
chesonno

(e.g.~\citealt{whiterees1978,khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}), 

@@

The existence of intermediate-scale stellar discs reveals a continuum of disc sizes, 
rather than a dichotomy of nuclear versus large-scale discs. 
The presence of intermediate-scale discs also blurs the distinction between elliptical and lenticular galaxies 
and creates the need for a new subclass to help bridge the divide. 
The existence of such discs is not only important for our understanding of disc growth in general, 
but accounting for such structure will impact our understanding of galaxy structure, 
with important consequences for galaxy scaling relations. 
%It has recently been argued that the classification scheme for elliptical galaxies should not be their apparent axis ratio as seen on the plane of the sky, 
%but instead their spheroid-to-total ratio, with a continuum from pure elliptical galaxies to disc-dominated lenticular galaxies \citep{graham2014review}.

@@

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of ellicular galaxies are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} are small. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in Savorgnan \& Graham (2015).
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis length $R_{\rm maj} \sim 15~\rm arcsec$).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. 
In comparison,

\subsection{NGC 1332}
The morphology of NGC 1332 (Figure \ref{fig:n1332}) is very similar to that of NGC 3115, 
with the ellipticity profile indicating the presence of an intermediate-scale disc, 
although in this case no nuclear component was identified from our photometric analysis. 
The authors of this paper were not able to find any extended kinematic profile or map 
for this galaxy in the literature. 
The data within the innermost $6~\rm arcsec$ were excluded from the fit 
because possibly affected by the presence of a partially depleted core.
The surface brightness profile of NGC 1332 is well described with a S\'ersic-spheroid plus
a $n<1$ S\'ersic-disc. 
Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
with a spheroid-to-total ratio of $0.95$.
\cite{rusli2011} did not identify the extent of the intermediate-scale disc, 
and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
with a spheroid-to-total ratio of $0.43$.
Based on such bulge-disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
by an order of magnitude along the black hole mass direction. 
However, in Section \ref{sec:mm} we show that, according to our decomposition, 
NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
for early-type galaxies.

\subsection{Mrk 1216}
Although the disc in the galaxy Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
the velocity map \citep{yildirim2015} proves the presence of a fast rotating component 
at least within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
The ellipticity profile (Figure \ref{fig:m1216}) indicates the presence of an intermediate-scale disc. 
In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$) 
and from a clear feature in the fourth harmonic profile (not shown here). 
We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
an intermediate-sized exponential-disc, and a nuclear exponential-disc.

\subsection{Other galaxies}
Our models with an intermediate-sized disc embedded within a larger spheroidal component, 
plus an additional nuclear component when one is present, 
match the observed light distribution, and explain both the extended kinematic maps (when available, \citealt{arnold2014}) and the ellipticity profiles, 
of other galaxies for which a direct measurement of their central supermassive black hole mass is available: 
NGC 821; NGC 1271; NGC 1277; NGC 3377; and NGC 4697. 
Our isophotal analysis and galaxy decompositions for NGC 1271 and NGC 1277 will be presented in 
Graham, Savorgnan \& Ciambur (\emph{in prep.}) and Graham et al.~(\emph{in prep.}), respectively, 
while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in Savorgnan \& Graham (\emph{submitted}).

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
\caption{The galaxy NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = S\'ersic (disc), gray = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n1332_image}
\includegraphics[width=0.49\columnwidth]{images/n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
\caption{The galaxy NGC 1332. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit.   
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = S\'ersic (disc). 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:n1332}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
\caption{The galaxy Mrk 1216. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$).
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = exponential (disc). 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:m1216}
\end{center}
\end{figure}

\section{Implications}
\label{sec:impl}
Past models that ``forcedly'' described ellicular galaxies using an inner bulge 
encased within a large-scale disc 
commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
and underestimate the size of the spheroid by a factor of $6-10$, 
although more ``extreme'' cases can be found. \\
\cite{lasker2014data} fit the galaxy NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$; 
we described this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtained a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. \\
\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$. \\
\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$. \\
The galaxy NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + inner disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$.

\subsection{The black hole -- spheroid correlation}

@@

i.e.~their central supermassive black hole has been reported to be 
over-massive compared to expectations from the spheroid luminosity (or stellar mass).

@@

In addition to these, also the elliptical galaxy NGC 4291 has been claimed to be a $\sim$$3.6\sigma$ outlier 

@@

for placing systems in the (black hole mass)-(spheroid mass) diagram. 
\emph{For early-type galaxies, the spheroid luminosity and the galaxy luminosity 

@@

Savorgnan et al.~(\emph{submitted}) shows that, when considering all galaxies irrespective of their morphological type, 

@@

(Savorgnan et al.~submitted). 

@@

Indeed, none of the five galaxies mentioned before (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 4291) is a noticeable outlier 

@@

In Figure \ref{fig:mm} we show the location of these five galaxies in the (black hole mass)-(spheroid stellar mass) diagram 
for early-type galaxies of Savorgnan et al.~(\emph{submitted}). 
Figure 4 was populated using a galaxy decomposition technique extensively described in Savorgnan \& Graham (\emph{submitted}). 

@@

We modelled their one-dimensional surface brightness profiles with a combination of analytic functions, using one function per galaxy component. 
Spheroid luminosities were converted into stellar masses using individual, but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014-MNRAS}). 
In addition, we show the galaxies Mrk 1216, NGC 1271 and NGC 1277, which were not a part of the original sample of 45.
For the galaxy NGC 1271, we use the black hole mass measurement and the mass-to-light ratio obtained by \cite{walsh2015}. 
The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition 
of Graham, Savorgnan \& Ciambur (\emph{in prep.}),  
who used an archived \emph{HST} image taken with the WFC3 and the near-infrared \emph{F160W} filter. 

@@

and the mass-to-light ratio obtained by \cite{martinnavarro2015}. 
The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition of Graham et al.~(\emph{in prep.}), 
who used an archived \emph{HST} image taken with the Advanced Camera for Surveys (\emph{ACS}) and the \emph{F550M} filter. 
For the galaxy Mrk 1216, we use the upper limit on the black hole mass and the mass-to-light ratio obtained by \cite{yildirim2015}. 
The luminosity of the spheroidal component of this galaxy comes from our one-dimensional spheroid/disc decomposition (Figure \ref{fig:m1216}).
For the first time, Figure \ref{fig:mm} reveals that when these five galaxies are properly modeled, 

@@

>>>>

(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}), 

@@

{\bf This paper is structured as follows. 
In Section \ref{sec:gal} we present a detailed photometric analysis of three ellicular galaxies (Mrk 1216, NGC 1332, and NGC 3115) 
and we briefly describe other five ellicular galaxies (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697). 
We compare our photometric analysis with the kinematical information available from the literature 
and explain the differences between our galaxy models and past decompositions. 
In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram. 
In Section \ref{sec:disc} we discuss our results in terms of galaxy evolution 
and we update the Hubble grid with the inclusion of ellicular galaxies. }

@@

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of ellicular galaxies are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in the presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} 
are small for these two galaxies. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in Savorgnan \& Graham (2015).
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis length $R_{\rm maj} \sim 15~\rm arcsec$).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

\subsection{NGC 1332}
The morphology of NGC 1332 (Figure \ref{fig:n1332}) is very similar to that of NGC 3115, 
with the ellipticity profile indicating the presence of an intermediate-scale disc, 
although in this case no nuclear component is evident. 
We were not able to find any extended kinematic profile or map 
for this galaxy in the literature. 
The data within the innermost $6~\rm arcsec$ were excluded from the fit 
because, according to our galaxy decomposition, they are possibly affected by the presence of a partially depleted core.
The surface brightness profile of NGC 1332 is well described with a S\'ersic-spheroid plus
an $n<1$ S\'ersic-disc. 
Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
with a spheroid-to-total ratio of $0.95$. \\
\cite{rusli2011} did not identify the restricted extent of the intermediate-scale disc, 
as revealed by the ellipticity profile, 
and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
with a spheroid-to-total ratio of $0.43$.
Based on their bulge/disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
by an order of magnitude along the black hole mass direction. 
However, in Section \ref{sec:mm} we show that, according to our decomposition, 
NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
for early-type galaxies. 
{\bf We also note that the majority of galaxies with an elevated stellar velocity dispersion ($\sigma > 270~\rm km~s^{-1}$) 
are core-S\'ersic galaxies \citep{graham2003coresersicmodel,trujillo2004coresersicmodel,dullograham2014cores}, 
i.e.~they have a partially depleted core which has been identified from high-resolution photometric data. 
NGC 1332 has $\sigma = 320~\rm km~s^{-1}$, but, 
based on their decomposition of \emph{HST} imaging, \cite{rusli2011} did not find a core in this galaxy. 
However, the identification of a partially depleted core is model dependent, 
that is, only a correct galaxy decomposition can confirm or rule out the presence of a core. 
Our galaxy decomposition (Figure \ref{fig:n1332}) suggests that NGC 1332 is in fact a core-S\'ersic galaxy. 
Since we did not use high-resolution photometric data, 
we refrain from a firm conclusion, 
but we caution that a re-analysis of the \emph{HST} data -- by taking into account the correct radial extent of the intermediate-scale disc --
may indeed reveal the presence of a core.}

\subsection{Mrk 1216}
Although the disc in the galaxy Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
the velocity map \citep{yildirim2015} reveals the presence of a fast rotating component 
within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
The ellipticity profile (Figure \ref{fig:m1216}), 
which extends out to five half-light radii, indicates the presence of an intermediate-scale disc. 
In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$), 
from the unsharp mask, 
and from a clear feature in the $B4$ fourth harmonic profile (not shown here). 
We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
an intermediate-sized exponential-disc, and a nuclear exponential-disc.

\subsection{Other galaxies}
Our models with an intermediate-sized disc embedded within a larger spheroidal component, 
plus an additional nuclear component when one is present, 
match the observed light distribution, and explain both the extended kinematic maps (when available, \citealt{arnold2014}) and the ellipticity profiles, 
of five additional galaxies for which a direct measurement of their central supermassive black hole mass is available: 
NGC 821; NGC 1271; NGC 1277; NGC 3377; and NGC 4697. 
Our isophotal analysis and galaxy decompositions for NGC 1271 and NGC 1277 will be presented in 
Graham, Savorgnan \& Ciambur (\emph{in prep.}) and Graham et al.~(2015), respectively, 
while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in Savorgnan \& Graham (2015).

\subsubsection{NGC 1271}
{\bf \cite{walsh2015} explored a three-component decomposition for NGC 1271 
and identified the galaxy bulge with the innermost of the three components, 
having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total ratio of $0.23$; 
our model features a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total ratio of $0.67$. }

\subsubsection{NGC 1277}
\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$.

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$.

\subsubsection{NGC 821}
\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$.

\subsubsection{NGC 4697}
The galaxy NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$. \\

Past models that ``forcedly'' described ellicular galaxies using an inner bulge 
encased within a large-scale disc 
commonly required the addition of an extended envelope or halo to account for the outer portion of the spheroid. 
Such three-component models (bulge + disc + envelope) typically reduce the spheroid luminosity by a factor of $3-4$, 
and underestimate the size of the spheroid by a factor of $6-10$, 
although more ``extreme'' cases can be found.

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
\caption{NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = S\'ersic (disc), gray = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n1332_image}
\includegraphics[width=0.49\columnwidth]{images/n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
\caption{NGC 1332.
Same as Figure \ref{fig:n3115}, except for the following. 
The surface brightness profile extends out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit. 
%The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
%obtained by dividing the image by a Gaussian-smoothed version of itself. 
%The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
%and the ellipticity profile, $\epsilon$, 
%along the major-axis, $R_{\rm maj}$. 
%The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
%The empty points are data excluded from the fit.   
%The color lines represent the individual (PSF-convolved) model components: 
%red = S\'ersic (spheroid), blue = S\'ersic (disc). 
%The residual profile (data $-$ model) is shown as $\Delta \mu$. 
%The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
%$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:n1332}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
\caption{Mrk 1216. 
Same as Figure \ref{fig:n3115}, except for the following. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
The surface brightness profile extends out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components:
red = S\'ersic (spheroid), blue = exponential (disc).
%The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right),
%obtained by dividing the image by a Gaussian-smoothed version of itself.
%The bottom plots display the best-fit model of the surface brightness profile, $\mu$,
%and the ellipticity profile, $\epsilon$,
%along the major-axis, $R_{\rm maj}$.
%The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$).
%The color lines represent the individual (PSF-convolved) model components:
%red = S\'ersic (spheroid), blue = exponential (disc).
%The residual profile (data $-$ model) is shown as $\Delta \mu$.
%The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations.
%$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:m1216}
\end{center}
\end{figure}

\section{The black hole -- spheroid correlation}

@@

i.e.~the mass of their central supermassive black hole has been reported to be significantly larger 
than what is expected from the galaxy's spheroid luminosity (or stellar mass).

@@

In addition to these, the elliptical galaxy NGC 4291 has also been claimed to be a $\sim$$3.6\sigma$ outlier 

@@

for placing systems in the (black hole mass)-(spheroid mass) diagram. \\
\emph{At present, for early-type galaxies, the spheroid luminosity and the galaxy luminosity 

@@

Savorgnan et al.~(2015) shows that, when considering all galaxies irrespective of their morphological type, 

@@

(Savorgnan et al.~2015). 

@@

Indeed, none of the five galaxies just mentioned (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 4291) is a noticeable outlier 

@@

In Figure \ref{fig:mm} we show the location of these five galaxies in the updated (black hole mass)-(spheroid stellar mass) diagram 
for early-type galaxies from Savorgnan et al.~(2015). 
Figure \ref{fig:mm} was populated using the galaxy decomposition technique shown here 
and extensively described in Savorgnan \& Graham (2015). 

@@

We modelled their one-dimensional surface brightness profiles with a combination of analytic functions, 
using one function per galaxy component. 
Spheroid luminosities were converted into stellar masses using individual, 
but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014-MNRAS}). \\
In Figure \ref{fig:mm}, we show the galaxies Mrk 1216, NGC 1271 and NGC 1277, 
which were not a part of the original sample of 45 early-type galaxies.
For the galaxy NGC 1271, we use the black hole mass measurement 
and the stellar mass-to-light ratio obtained by \cite{walsh2015}. 
%The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition 
%of Graham, Savorgnan \& Ciambur (\emph{in prep.}),  
%who used an archived \emph{HST} image taken with the WFC3 and the near-infrared \emph{F160W} filter. 

@@

and the stellar mass-to-light ratio obtained by \cite{martinnavarro2015}. 
%The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition of Graham et al.~(\emph{in prep.}), 
%who used an archived \emph{HST} image taken with the Advanced Camera for Surveys (\emph{ACS}) and the \emph{F550M} filter. 
For the galaxy Mrk 1216, we use the upper limit on the black hole mass 
and the stellar mass-to-light ratio obtained by \cite{yildirim2015}. 
%The luminosity of the spheroidal component of this galaxy comes from our one-dimensional spheroid/disc decomposition (Figure \ref{fig:m1216}).
For the first time, Figure \ref{fig:mm} reveals that when the four ellicular galaxies Mrk 1216, NGC 1271, NGC 1277, NGC 1332, 
and the elliptical galaxy NGC 4291 are properly modeled, 

@@

\section{Conclusions}
{\bf I'll write them after the first ref. rep. :) }
